Identifying regime transitions for water governance at a basin scale

### 2022-04-28 paper/main/01_introduction.tex
feat(references): update all references
BREAKING CHANGE:

\label{Intro.}
Water, being ``at the centre of the planetary drama of the Anthropocene'' \cite{gleesonIlluminatingwatercycle2020}, is essential not only for earth system processes but also in supporting development and human well-being.
As an integral part of a proposed earth system governance framework, water governance requires a deep understanding of changes in the complex relationships between humans and water
\cite{dibaldassarreSociohydrologyScientificChallenges2019,biermannNavigatingAnthropoceneImproving2012,steffenemergenceevolutionEarth2020}.
Human activities stemming from our reliance on the water have profoundly modified the natural water cycle, resulting in rivers dominated by a hybrid of social and natural tendencies
\cite{gleesonIlluminatingwatercycle2020,sivapalanSociohydrologynewscience2012,qinTheoreticalframeworkdualistic2014,abbottwatercycleAnthropocene2019,leviaHomogenizationterrestrialwater2020}.
Facing this transition, many big river basins worldwide (which are hot spots of civilization and economic growth) are urgently in need of successful water governance for sustainability
\cite{bestAnthropogenicstressesworld2019,falkenmarkUnderstandingwaterresilience2019,dibaldassarreSociohydrologyScientificChallenges2019}.

Water governance refers to the political, social, economic, and administrative systems that influence the use and management of water %! citation.
For populated large river basins, missing governance means missing sustainability, and a first important step in understanding the transitions with successful water governance is identifying the different regimes.
\cite{undpwatergovernancefacilityWaterGovernanceIssue}.
Regimes of water governance maintained by concreted intertwine within human-water systems (such as management, institutions, and exploitations), as a stable state in structures and functions
\cite{carpenterEarlyWarningsRegime2011,rochaCascadingregimeshifts2018, gregrCascadingsocialecologicalcosts2020}.
Therefore, regime shifts sometimes lead to new water governance challenges as both signals and consequences of substantive changes in human-water systems.
The lack of a comprehensive but straightforward approach to identifying changes in water governance regimes challenges sustainability, and filling this gap can well align human and water systems (Figure~\ref{fig:framework}).

Governance is essentially about ``who gets what, when and how''. The United Nations Development Programme (UNDP) thus suggested that three key dimensions of water use are decided by the water governance directly: ``When and what water to use?'' (stress), ``How does water provides different services to well-beings?'' (purpose), and ``Who can use water equally and efficiently?'' (allocation)
\cite{undpwatergovernancefacilityWaterGovernanceIssue, mariajacobsonUserguideassessing2013, kjellenWatergovernanceperspective2015}. %! UNDP year
First, water stress depends not only on climate (with increasing scarcity and uncertainty in many regions) but also on the increasingly insatiable demands from economic activities such as irrigation and industry; water storage can resolve some but not all of these issues
\cite{greveGlobalassessmentwater2018,wadaHumanwaterinterface2017,qinFlexibilityintensityglobal2019}.
Second, the purpose of how water services human well-being is to consider trade-offs between consumptive uses (e.g., drinking and food production) and non-consumptive uses (e.g., energy production)
\cite{liuWaterscarcityassessments2017,florkeWatercompetitioncities2018,kleemannQuantifyinginterregionalflows2020}.
Third, the allocation of water across the whole basin is not only decided by regionally socio-economic and environmental context but also influenced by systematically regulating
\cite{roobavannanRoleSectoralTransformation2017,speedBasinwaterallocation2013}.
Despite regime shifts in water governance related to substantive changes in any of the three dimensions, separately considering their intertwines within human-water systems can lead to holistic failure in governing water.

The Yellow River Basin (YRB), the fifth-largest river in the world, was most in need of integrated water governance because drastically anthropogenic intervention led to intense governance challenges in sustainability (see \textit{Appendix} Methods S1 and Figure S1 for details).
Since the 1960s, the implementation of conservation measures, regulation reservoirs, and levee constructions have contained the governance issues troubled by thousands of years of high sediment loads
\cite{wangReducedsedimenttransport2016,wuEvolutioneffectssocialecological2020}.
However, decreased streamflows and water over-use then led to depletions of the over-burdened river, creating new challenges and new governance practices, including water use regulation and water transfer across basins
\cite{xiaDevelopmentWaterAllocation2012}.
Today, it is still impossible to completely solve water stress, trade-offs between ecosystem services, or lopsided development in different regions in the YRB; -``who gets water, when and how‘’ is always an open question for sustainable development
\cite{wangYellowRiverwater2019,wohlfartSocialecologicalchallengesYellow2016}.
Confronting governance challenges induced by environmental, economic, social, and political factors, numerous governance practices have led the YRB to be among the most drastically-governing large river basins worldwide
Identifying regime shifts in water governance within the YRB can thus provide crucial insights into rapidly-changing big river basins and how governance may respond to meeting challenges to their sustainability.

>>>>

\label{Intro.}
Water, being ``at the centre of the planetary drama of the Anthropocene'', is essential not only for earth system processes but also in supporting the development and human well-being
\cite{gleeson2020a,gleeson2020b}.
As an integral part of earth system governance, water governance requires a deep understanding of changes in the complex relationships between humans and water
\cite{ahlstrom2021,biermann2012,steffen2020}.
Human activities stemming from our reliance on the water have profoundly modified the natural water cycle, resulting in rivers dominated by a hybrid of social and natural tendencies
\cite{sivapalan2012,qin2014,abbott2019}.
Facing this transition, many big river basins worldwide (which are hot spots of civilization and economic growth) are urgently in need of successful water governance for sustainability
\cite{best2019,dibaldassarre2019}.

Water governance refers to the political, social, economic, and administrative systems that influence the use and management of water \cite{oecd2018, wang2017}.
For populated large river basins, missing governance means missing sustainability, and a first important step in understanding the transitions with successful water governance is identifying the different regimes \cite{kjellen2015, grafton2013}.
Regimes of water governance maintained by concreted intertwine within human-water systems (such as management, institutions, and exploitations), as a stable state in structures and functions
\cite{falkenmark2021,bressers2013,loch2020}.
Therefore, regime shifts sometimes lead to new water governance challenges as both signals and consequences of substantive changes in human-water systems.
The lack of a comprehensive but straightforward approach to identifying changes in water governance regimes challenges sustainability, and filling this gap can well align human and water systems (Figure~\ref{fig:framework}).

Governance is essentially about ``who gets what, when and how''\cite{lasswell2018}. The United Nations Development Programme (UNDP) thus suggested that three key dimensions of water use are decided by the water governance directly: ``When and what water to use?'' (stress), ``How does water provides different services to well-beings?'' (purpose), and ``Who can use water equally and efficiently?'' (allocation)
\cite{undpwatergovernancefacility2016}.
First, water stress depends not only on climate (with increasing scarcity and uncertainty in many regions) but also on the increasingly insatiable demands from economic activities such as irrigation and industry; water storage can resolve some but not all of these issues
\cite{qin2019,wada2014,huang2021}.
Second, the purpose of how water services human well-being is to consider trade-offs between consumptive uses (e.g., drinking and food production) and non-consumptive uses (e.g., energy production)
\cite{liu2017,florke2018,jaeger2019}.
Third, the allocation of water across the whole basin is not only decided by regionally socio-economic and environmental context but also influenced by systematically regulating
\cite{schmandt2021,speed2013}.
Despite regime shifts in water governance related to substantive changes in any of the three dimensions, separately considering their intertwines within human-water systems can lead to holistic failure in governing water.

The Yellow River Basin (YRB), the fifth-largest river in the world, was most in need of integrated water governance because drastically anthropogenic intervention led to intense governance challenges in sustainability
\cite{mostern2021}.
Since the 1960s, the implementation of conservation measures, regulation reservoirs, and levee constructions have contained the governance issues troubled by thousands of years of high sediment loads
\cite{wang2016e,song2020a}.
However, decreased streamflows and water over-use then led to depletions of the over-burdened river, creating new challenges and new governance practices, including water use regulation and water transfer across basins
\cite{wang2019c}.
Today, it is still impossible to completely solve water stress, trade-offs between ecosystem services, or lopsided development in different regions in the YRB; -``who gets water, when and how'' is always an open question for sustainable development
\cite{wohlfart2016a}.
Confronting governance challenges induced by environmental, economic, social, and political factors, numerous governance practices have led the YRB to be among the most drastically-governing large river basins worldwide \cite{nickum2021}.
Identifying regime shifts in water governance within the YRB can thus provide crucial insights into rapidly-changing big river basins and how governance may respond to meeting challenges to their sustainability.

### 2022-04-28 paper/main/02_methods.tex
feat(references): update all references
BREAKING CHANGE:

	\subsubsection*{Indicator of stress}
	We used the scarcity-flexibility-variability (SFV) water stress index proposed in Qin et al., 2019 to evaluate water stress ($SFV_i$) as the Indicator in a particular region $i$ \cite{qinFlexibilityintensityglobal2019}. This metric takes into account management measures (such as the construction of reservoirs) and the impact of changes in the industrial structure of water use on the evaluation of water scarcity (see \textit{SI Appendix} Methods S4 for details). For the whole YRB, the indicator of water stress $I_S$ is the average of all regions' SFV-index:
	\begin{equation}
		I_S = \frac{1}{4} * \sum_{i=1}^4 SFV_{i}
	\end{equation}

@@

		With no assumptions about the distribution of the data, we applied the Pettitt (1979) approach of change-point detection to detect a single change-point in hydrological time series with continuous data
        \cite{pettittNonParametricApproachChangePoint1979}.
		It tests $H0$: The variables follow one or more distributions with the exact location parameter (no change) against the alternative: a change point exists.
		Mathematically, when a sequence of random variables is divided into two segments represented by $\mathrm{x}_{1}, \mathrm{x}_{1}, \ldots, x_{t_{0}} \text{and} x_{t_{0}+1}, x_{t_{0}+2}, \ldots, x_{T}$, if each segment has a common distribution function, i.e., $F_1(x)$, $F_2(x)$ and $F_1(x) \neq F_2(x)$, then the change point is identified at $t_0$. To achieve the identification of change point, a statistical index $U_{t,T}$ is defined as follows:

>>>>

	\subsubsection*{Indicator of stress}
	We used the scarcity-flexibility-variability (SFV) water stress index proposed in Qin et al., 2019 to evaluate water stress ($SFV_i$) as the Indicator in a particular region $i$ \cite{qin2019}. This metric takes into account management measures (such as the construction of reservoirs) and the impact of changes in the industrial structure of water use on the evaluation of water scarcity (see \textit{SI Appendix} Methods S4 for details). For the whole YRB, the indicator of water stress $I_S$ is the average of all regions' SFV-index:
	\begin{equation}
		I_S = \frac{1}{4} * \sum_{i=1}^4 SFV_{i}
	\end{equation}

@@

		With no assumptions about the distribution of the data, we applied the Pettitt (1979) approach of change-point detection to detect a single change-point in hydrological time series with continuous data
        \cite{pettitt1979}.
		It tests $H0$: The variables follow one or more distributions with the exact location parameter (no change) against the alternative: a change point exists.
		Mathematically, when a sequence of random variables is divided into two segments represented by $\mathrm{x}_{1}, \mathrm{x}_{1}, \ldots, x_{t_{0}} \text{and} x_{t_{0}+1}, x_{t_{0}+2}, \ldots, x_{T}$, if each segment has a common distribution function, i.e., $F_1(x)$, $F_2(x)$ and $F_1(x) \neq F_2(x)$, then the change point is identified at $t_0$. To achieve the identification of change point, a statistical index $U_{t,T}$ is defined as follows:

### 2022-04-28 paper/main/04_discussion.tex
feat(references): update all references
BREAKING CHANGE:

% Implications
Water governance gradually becomes a national or international concern from a primarily local concern because large river basins are critical sources of ecosystem services, economic development, and human well-being.
As the ubiquitous tele-coupling is rising additional water governance challenges in the tighter connected world, the transition of hydrosocial cycle and regime shifts align with different human-water relationships.
The process echoes how societies can change governance practices by enhancing their adaptive capacity in the hydrosocial cycle, and the IWGI quantitatively identifies this transition.
It is important for scientists and decision-makers to recognize the changing governance challenges because models, institutions, engineering, and approaches developed under one regime are not necessarily useful under a different regime
%* \cite{cummingLinkingEconomicGrowth2018, reyersSocialEcologicalSystemsInsights2018}.

% 我们为的研究结果表明，黄河流域能被识别为三个明显的稳态。
In the case of the YRB, our results show that there have been three distinct but sequential governance regimes: a massive supply regime (P1: 1965-1978), a governance transforming regime (P2: 1979-2001) and an adaptation oriented regime (P3: 2002-2013).
During the massive supply regime with lower water stress (1965-1978 in the YRB), water governance thus tended to boost water supply for services (mainly provisioning purposes then -livestock and crops) by constructing reservoirs and channels.
As the popular slogan ``man will conquer nature'' suggested, however, the enhancement of water supply aligned with little consideration of the irreversible changes in the human-water relationship, thus drastically increasing water demand with little consideration in basinal conservation
\cite{zhouDecelerationChinahuman2020}.
The rapid expansion of irrigated farmland and water diversion facilities in that decade brought the overburdened YRB close to the critical point, where keeping increasing supply to meet the unlimited demand is unpractical
As a result, the over 80\% surface water use then led to river depletions frequently since 1972, with ecological issues, such as wetlands shrinkage and declines in biodiversity.
In addition, as the water stress also limited the industrial economy in the ascendant, the existing modes of water governance led to a social-ecological crisis and challenged sustainability rigorously
\cite{wohlfartRiverBasinCourse2016}.

The start of the governance transforming regime (P2: 1979-2001) coincided with the rising competition for water use after the ``reform and opening-up''.
% 正如理论预测的那样
The results in the YRB keep in line with the suggestions from the theoretical analysis: continuous increases in water demand when the basinal total supply is stable can follow substantial changes in governance regime and the rapid enhancement in overall social adaptive capacity %! Citation.
% 作为制度转变的先行者
Being a pioneer in shifting governing institutions, the YRB triggered a series of changes in ``who gets water, when and how'' during this regime: slowing growth of irrigated acreage; leading water-saving infrastructure; China's first water quota scheme; The preliminary cross-boundaries water transfer plan and so on
\cite{wangThirtyYearsYellow2018}.
% 因此，1999年黄河的最后一次枯竭
Consequently, though water stress remained and increased (mainly led by reducing streamflow and flexibility), the last depletion of the Yellow River in 1999 added a footnote to the climax of this transformation in water governance.

When it came to an adaptation-oriented regime (P3: 2002-2013), drastically shifting in societies adapted to the stable high water stress.
Socio-economic trade-offs between water-dependent regions and sectors played a more important role in this regime, so water governance had to achieve efficient water allocation while balancing different purposes in the face of limited water supply
\cite{dalinBalancingwaterresource2015}.
Reconstruction of resources widespread in different industries and regions was calling for adaptation in water governance, where the urgent requirements of adjusting the rigid quota shares from the previous regime can be an example.
Like this, many national-level governing practices were proposed under the regime because the absence of such policies with the social dilemma of high-quality development became new structural challenges for water governance
\cite{konarExpandingScopeFoundation2019}.

% 总体而言，长江流域的水治理是“改善供给、转变治理、增强适应”的水社会循环总体转型中最突出的例子之一。
In general, water governance of the YRB is among the most prominent example in the general transition of hydrosocial cycle -``improving supply, transforming governance, and enhancing adaptation''.
With each dimension changing gradually, the emergence of regime shifts drives the water governance challenges at a basin-scale: primarily economic and environmental before the transformation but social and policy-related towards the end (Figure~\ref{fig:summary}) \cite{singhWaterGovernanceChallenges2019,porcherFacingChallengesWater2019}.
In the analogy at a global scale, the resource challenges, represented as water shortage and water supplying difficulties, are mainly faced by undeveloped and developing basins
\cite{allanNavigatingcomplexitiescoordinated2019,florkeWatercompetitioncities2018,liuWaterSustainabilityChina2012}.
Alternatively, highly-controlled and developed basins (especially for transboundary rivers) must mainly resolve structural challenges, such as water disputes or lack of equity, and may be in urgent need of novel flexible, efficient sociopolitical governance structures %* Kitroeff citation wrong
\cite{kitroeffThisWarCrossBorder2020,kitroeffThisWarCrossBorder2020,roobavannanRoleSectoralTransformation2017,unep-dhiTransboundaryRiverBasins2016}.
Linking regime shifts to the governance challenges, the implementation of IWGI thus offers a comprehensive and straightforward way to interpret the intertwines between water governance and the hydrosocial transition.

%* limitations & direction
One of the main limitations in the approach is the few data worldwide with a long-term period, which means still a gap between the comprehensively identifying and widespread application of IWGI.
However, we assumed that all water governance issues are relative to ``who gets water, when and how'', so water stress, purposes of water services, and water allocation patterns matter.
We suggest that choices of the indicators for the dimensions, therefore, can be adapted according to available datasets as the intertwines between the underlying components are much more crucial in understanding the transition of governance regimes holistically
\cite{steffenemergenceevolutionEarth2020,muneepeerakulemergenceresilienceselforganized2020,bodinCollaborativeenvironmentalgovernance2017,biermannNavigatingAnthropoceneImproving2012}.
In today's world, the regime shifts from biophysical to hydrosocial control of dynamics may become increasingly widespread, so the comprehensive strategies to address governance challenges have become the core of complex human-water systems
\cite{bestPaceHumanInducedChange2020,cummingLinkingeconomicgrowth2018,cummingImplicationsagriculturaltransitions2014}.
Although river basins have shown improvements in water management technologies and water use efficiency, many of them are still approaching planetary boundaries where human-water systems may collapse
\cite{anExploringeffectsGrain2017,degraafEnvironmentalflowlimits2019,hugginssocialecologicaldimensionschanging2020}.
A deeper understanding of governance that incorporates ideas of non-linear regime shifts and transformations should help to shift the focus of governance towards maintaining the resilience of the basin’s social-ecological system and improving its sustainability.

>>>>

% Implications
Water governance gradually becomes a national or international concern from a primarily local concern because large river basins are critical sources of ecosystem services, economic development, and human well-being \cite{best2019, best2020}.
As the ubiquitous tele-coupling is rising additional water governance challenges in the tighter connected world, the transition of hydrosocial cycle and regime shifts align with different human-water relationships \cite{diaz2019}.
The process echoes how societies can change governance practices by enhancing their adaptive capacity in the hydrosocial cycle, and the IWGI quantitatively identifies this transition \cite{loch2020,turton1999}.
It is important for scientists and decision-makers to recognize the changing governance challenges because models, institutions, engineering, and approaches developed under one regime are not necessarily useful under a different regime \cite{reyers2018}.

% 我们为的研究结果表明，黄河流域能被识别为三个明显的稳态。
In the case of the YRB, our results show that there have been three distinct but sequential governance regimes: a massive supply regime (P1: 1965-1978), a governance transforming regime (P2: 1979-2001) and an adaptation oriented regime (P3: 2002-2013).
During the massive supply regime with lower water stress (1965-1978 in the YRB), water governance thus tended to boost water supply for services (mainly provisioning purposes then -livestock and crops) by constructing reservoirs and channels.
As the popular slogan ``man will conquer nature'' suggested, however, the enhancement of water supply aligned with little consideration of the irreversible changes in the human-water relationship, thus drastically increasing water demand with little consideration in basinal conservation
\cite{zhou2020}.
The rapid expansion of irrigated farmland and water diversion facilities in that decade brought the overburdened YRB close to the critical point, where keeping increasing supply to meet the unlimited demand is unpractical \cite{loch2020}.
As a result, the over 80\% surface water use then led to river depletions frequently since 1972, with ecological issues, such as wetlands shrinkage and declines in biodiversity \cite{wang2019c}.
In addition, as the water stress also limited the industrial economy in the ascendant, the existing modes of water governance led to a social-ecological crisis and challenged sustainability rigorously
\cite{wohlfart2016a}.

The start of the governance transforming regime (P2: 1979-2001) coincided with the rising competition for water use after the ``reform and opening-up''.
% 正如理论预测的那样
The results in the YRB keep in line with the suggestions from the theoretical analysis: continuous increases in water demand when the basinal total supply is stable can follow substantial changes in governance regime and the rapid enhancement in overall social adaptive capacity \cite{loch2020}.
% 作为制度转变的先行者
Being a pioneer in shifting governing institutions, the YRB triggered a series of changes in ``who gets water, when and how'' during this regime: slowing growth of irrigated acreage; leading water-saving infrastructure; China's first water quota scheme; The preliminary cross-boundaries water transfer plan and so on
\cite{wang2019a,long2020,nickum2021}.
% 因此，1999年黄河的最后一次枯竭
Consequently, though water stress remained and increased (mainly led by reducing streamflow and flexibility), the last depletion of the Yellow River in 1999 added a footnote to the climax of this transformation in water governance \cite{wang2019a}.

When it came to an adaptation-oriented regime (P3: 2002-2013), drastically shifting in societies adapted to the stable high water stress.
Socio-economic trade-offs between water-dependent regions and sectors played a more important role in this regime, so water governance had to achieve efficient water allocation while balancing different purposes in the face of limited water supply
\cite{dalin2015,song2022}.
Reconstruction of resources widespread in different industries and regions was calling for adaptation in water governance, where the urgent requirements of adjusting the rigid quota shares from the previous regime can be an example \cite{wang2019a}.
Like this, many national-level governing practices were proposed under the regime because the absence of such policies with the social dilemma of high-quality development became new structural challenges for water governance
\cite{konar2019}.

% 总体而言，长江流域的水治理是“改善供给、转变治理、增强适应”的水社会循环总体转型中最突出的例子之一。
In general, water governance of the YRB is among the most prominent example in the general transition of hydrosocial cycle -``improving supply, transforming governance, and enhancing adaptation''.
With each dimension changing gradually, the emergence of regime shifts drives the water governance challenges at a basin-scale: primarily economic and environmental before the transformation but social and policy-related towards the end (Figure~\ref{fig:summary}) \cite{singh2019,porcher2019}.
In the analogy at a global scale, the resource challenges, represented as water shortage and water supplying difficulties, are mainly faced by undeveloped and developing basins
\cite{allan2019,speed2013,liu2012a}.
Alternatively, highly-controlled and developed basins (especially for transboundary rivers) must mainly resolve structural challenges, such as water disputes or lack of equity, and may be in urgent need of novel flexible, efficient sociopolitical governance structures %* Kitroeff citation wrong
\cite{unep-dhi2016,mirumachi2015}.
Linking regime shifts to the governance challenges, the implementation of IWGI thus offers a comprehensive and straightforward way to interpret the intertwines between water governance and the hydrosocial transition.

%* limitations & direction
One of the main limitations in the approach is the few data worldwide with a long-term period, which means still a gap between the comprehensively identifying and widespread application of IWGI.
However, we assumed that all water governance issues are relative to ``who gets water, when and how'', so water stress, purposes of water services, and water allocation patterns matter.
We suggest that choices of the indicators for the dimensions, therefore, can be adapted according to available datasets as the intertwines between the underlying components are much more crucial in understanding the transition of governance regimes holistically.
In today's world, the regime shifts from biophysical to hydrosocial control of dynamics may become increasingly widespread, so the comprehensive strategies to address governance challenges have become the core of complex human-water systems
\cite{cumming2018,cumming2014,jaeger2019}.
Although river basins have shown improvements in water management technologies and water use efficiency, many of them are still approaching planetary boundaries where human-water systems may collapse
\cite{gleeson2020, wang-erlandsson2022}.
A deeper understanding of governance that incorporates ideas of non-linear regime shifts and transformations should help shift the focus of governance towards maintaining the resilience of the basin’s social-ecological system and improving its sustainability
\cite{falkenmark2019}.

### 2022-04-28 paper/main/manuscript.tex
feat(references): update all references
BREAKING CHANGE:

%%\documentclass[sn-basic]{sn-jnl}% Basic Springer Nature Reference Style/Chemistry Reference Style
% \documentclass[sn-mathphys]{sn-jnl}% Math and Physical Sciences Reference Style
%%\documentclass[sn-aps]{sn-jnl}% American Physical Society (APS) Reference Style
%%\documentclass[sn-vancouver]{sn-jnl}% Vancouver Reference Style
%%\documentclass[sn-apa]{sn-jnl}% APA Reference Style
%%\documentclass[sn-chicago]{sn-jnl}% Chicago-based Humanities Reference Style
% \documentclass[sn-standardnature]{sn-jnl}% Standard Nature Portfolio Reference Style
% \documentclass[default]{sn-jnl}% Default
\documentclass[default,iicol]{sn-jnl}% Default with double column layout

@@

\abstract{
    In many large river basins, water governance regimes from natural to social-ecological or `hydrosocial' situations profoundly change who gets water, when, and how.
    Identifying changes in governance regimes is critical to understanding the transition and guiding the efficient and sustainable use of water.
    We combined three main dimensions of water governance (supply, purpose and allocation) to develop a quantitative Integrated Water Governance Index (IWGI) to detect regime shifts in water governance at a basin scale.
    Applying the index to a rapidly-changing large river basin (the Yellow River Basin, China) describes how water governance shifts between three regimes over half a century. (massive supply regime; governance transformation regime; and adaptation oriented regime, respectively).
    In the YRB, the regime shifts' underlying causes are increasing water supply and demand through the construction of reservoirs and expansion of irrigated areas before the governance transformation, while are re-allocation and regulation after the transformation.
    Our application of the IWGI offers a comprehensive and straightforward way to link the water governance regimes to the hydrosocial transition, following challenges in sustainability.
}

>>>>

%%\documentclass[sn-basic]{sn-jnl}% Basic Springer Nature Reference Style/Chemistry Reference Style
% \documentclass[sn-mathphys]{sn-jnl}% Math and Physical Sciences Reference Style
%%\documentclass[sn-aps]{sn-jnl}% American Physical Society (APS) Reference Style
%%\documentclass[sn-vancouver]{sn-jnl}% Vancouver Reference Style
%%\documentclass[sn-apa]{sn-jnl}% APA Reference Style
%%\documentclass[sn-chicago]{sn-jnl}% Chicago-based Humanities Reference Style
% \documentclass[sn-standardnature]{sn-jnl}% Standard Nature Portfolio Reference Style
% \documentclass[default]{sn-jnl}% Default
\documentclass[default,iicol,lineno]{sn-jnl}% Default with double column layout

@@

\abstract{
    In many large river basins, water governance regimes from natural to social-ecological or `hydrosocial' situations profoundly change who gets water, when, and how.
    Identifying regime changes is critical to understanding the transition and guiding sustainability in water governance.
    We combined three main dimensions -stress, purpose and allocation- to develop a quantitative Integrated Water Governance Index (IWGI) to detect water governance regimes at a basin scale.
    Applying the IWGI to a rapidly-changing basin (the Yellow River Basin, China) describes how water governance shifts between the massive supply regime, governance transformation regime, and adaptation oriented regime.
    In the YRB, the regime shifts' underlying causes were increasing water supply and demand before the governance transformation and re-allocation and regulation after the transformation.
    The IWGI offers a comprehensive and straightforward approach to linking the water governance regimes to the following challenges in sustainability, along with the hydrosocial transition.
}
